---
title: "Group 03 CA pollution burden"
author: "Drew Andersen & Taylor Medina"
date: "11/15/2021"
output: html_document
---

**Data:** CalEnviroScreen 3.0 (2017). *California Environmental Justice Alliance*. https://caleja.org/wp-content/uploads/2015/09/CES3.0-5.pdf

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE , message = FALSE, warning = FALSE)

library(tidyverse)
library(janitor)
library(here)
```

```{r}
ces <- read_csv(here("data","ces3demographics.csv")) %>% 
  clean_names()
```

```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + 
  theme_minimal() +
  scale_fill_gradient(low = "purple", high = "red") +
  labs(x = "Percent White Population (%)",
       y = "CalEnviroScreen Score")
```

**Figure 1** Percent white population versus the aggregate CalEnviroScreen 3.0 score in California. The a higher count of populations for each hexxed bin is indicated by a redder hue. 

The overall trend is that as the white population increases, the CalEnviroScreen score decreases. A lower score means a better quality of life and the population associated with this score experience less pollution, social inequality, and economic inequality, so for this plot, a higher proportion of white residents is associated with a better quality of life. 
